\subsection{Limitations}

% physics
\subsubsection{Self-Leveling Flight Mode Only}

For implementation simplicity, the current system is limited to self-leveling flight dynamics. Although Yue's Ultimate Drone physics model supports both self-leveling and acrobatic modes, this study focuses exclusively on the former to align with the design of the human-AI collaboration agents, which are optimized for stable flight control.

Consequently, acrobatic behaviors are not supported in the current implementation, which restricts the system's applicability to advanced flight scenarios.

% xr
\subsubsection{Visual Feedback Only}

Extended reality (XR) systems can support multimodal feedback. In the present study, additional modalities, such as haptic feedback and spatial audio, were considered during the design phase of the human-AI collaboration system but were not implemented.

Although players may perceive the drone's position through its humming sound, no additional auditory or haptic feedback was provided.

This limitation is primarily due to the increased design complexity associated with determining appropriate feedback types, intensity levels, and integration strategies. These aspects remain open challenges for future research.

\subsubsection{No Public Participant Testing}

This study primarily focuses on system design and implementation rather than controlled user evaluation. As XR-based control interfaces remain relatively unfamiliar to many users, variability in prior experience may significantly influence task performance.

In addition, the evaluation is highly dependent on the deployment platform. WebXR-based applications rely on browser compatibility, standalone systems (e.g., Meta Quest) depend on proprietary platforms such as Horizon Store, and PCVR setups require users to configure their own desktop environments.

These factors make it difficult to isolate learning effects from interface unfamiliarity, thereby limiting the interpretability of the user study results.