\subsection{Design Methods and Development Strategy}

\subsubsection{Design-Based Research}

Design-based research (DBR) is a research methodology aimed at improving educational practices through systematic, flexible, and iterative processes of analysis, design, development, implementation, and evaluation. It is grounded in collaboration between researchers and practitioners in real-world settings, ultimately producing design principles or theoretical contributions \parencite{wang_influence_2026}.

DBR is primarily conducted in authentic educational environments to bridge the gap between theoretical research and practical application \parencite{jong_design-based_2017}. Unlike traditional laboratory-based approaches, DBR is situated in naturalistic contexts where social interactions and environmental complexity are preserved and considered as integral parts of the research process \parencite{wang_influence_2026}.

A central feature of DBR is its iterative cycle, which consists of design, enactment, analysis, and redesign. The outputs of each cycle inform and guide subsequent cycles, enabling continuous refinement of both the intervention and the underlying theory \parencite{jong_design-based_2017}.

% TODO: a graph

\subsubsection{Agile Development}

\textcite{Beck2004XP} define Agile as a set of values and principles that emphasize iterative development, customer collaboration, and responsiveness to change. Agile development approaches typically include iterative and incremental development, self-organizing teams, and continuous feedback and adaptation.

Agile processes focus on the rapid and early delivery of working software and are based on development models that support incremental and iterative progress \parencite{keith2010agile}.

A user story is a description of a feature expressed from the perspective of the user and its intended value. User stories serve as the core unit of work in Agile development. Multiple user stories are maintained in a backlog, from which a subset is selected for implementation during a time-boxed iteration, typically lasting two to four weeks, known as a sprint. A collection of related user stories that collectively deliver a larger functional capability is referred to as an epic. Completed sets of functionality, such as alpha or beta versions, are commonly referred to as milestones.

User stories must be estimated, which requires sufficient understanding of both the system being built and the implementation approach. If the scope of a story is too large or insufficiently understood, accurate estimation becomes difficult. Such cases are often addressed through spikes, which are time-boxed research tasks used to reduce uncertainty \parencite{keith2010agile}.

Both DBR and Agile share a common iterative philosophy, in which development proceeds through cycles of analysis, implementation, evaluation, and refinement, enabling continuous learning and adaptation throughout the process.