\subsubsection{Materials and Equipment: Game Assets, AI, and Tools}

This study employed a range of materials and technical tools to support the design and development processes described in previous sections.

\paragraph{Game Assets}

Several third-party game assets were integrated to enhance environmental guidance and visual fidelity. A directional signal asset was used to support navigation within the realistic environment \parencite{unity_env_track_lowpoly}. A skybox asset was applied to construct the virtual sky in the XR scenes \parencite{unity_fantasy_skybox}. Additionally, floor material assets were utilized to create visually realistic paved roads within the environment \parencite{unity_floor_materials}. Coin collecting assets were incorporated as visual cues to guide user navigation \parencite{unity_gems_items}.

Together, these assets enabled the project to achieve a baseline level of visual quality suitable for user interaction and environmental orientation.

\paragraph{Use of AI}

Large Language Models (LLMs) were extensively utilized throughout this study. ChatGPT was primarily used for grammatical refinement and alignment with APA 7 academic writing standards. NotebookLM was employed as a research support tool due to its strong Retrieval-Augmented Generation (RAG) capabilities \parencite{maniulit_learning_2026}. In addition, Claude Opus 4.6 and Cursor Composer 2 were used as coding assistants to support software development tasks. The Unity AI Assistant was further applied in conjunction with Model Context Protocol (MCP) workflows to facilitate the construction of the realistic city environment.

\paragraph{Tools Used}

The project source code was managed using Git and hosted on GitHub (see Appendix 1). Blender was used for 3D asset modeling, while QGIS was employed for processing and managing geospatial data used in the realistic environment generation.

To support the understanding of quadcopter physics, this study referenced technical documentation from BetaFPV \parencite{betafpv2022manual}. And the study used \parencite{yuetility2022fpvphysics} for final implementation.