
\subsubsection{Human-AI Collaboration}

% \subsubsection{Human-AI Collaboration}

Game AI, also referred to as 'AI in games', is a broad research field that studies the application of artificial intelligence within and for games \parencite{garcia-sanchez_georgios_2019}. It is widely used in both board games and video games. 

\textcite{dablander_future_2024} identify three major application domains of game AI: (1) non-player character (NPC) control and agent modeling, (2) procedural content generation, and (3) player modeling. More specifically, AI for game playing and agent modeling includes simulating human players or controlling in-game agents such as NPCs or environmental systems. AI-based procedural content generation focuses on the algorithmic creation of game elements, including levels, music, textures, dialogue, items, and characters. In addition, player modeling aims to infer player characteristics such as play style, behavioral patterns, or emotional states based on gameplay data.

In the intelligent era, the interaction between humans and intelligent systems fundamentally involves collaboration with autonomous intelligent agents. Human-AI Collaboration (HAC) represents a novel type of human-machine relationship facilitated by autonomous intelligent machines equipped with AI technologies. In this paradigm, AI agents serve not only as auxiliary tools but also as active teammates, partnering with humans to accomplish tasks collaboratively.\parencite{gao2025humancenteredhumanaicollaborationhchac}

One prominent form of HAC is mixed-initiative co-creativity (MI-CC), in which both humans and AI systems actively participate in the creative process. MI-CC systems have been applied in domains such as game design, programming (e.g., GitHub Copilot), visual art generation, and storytelling. Although MI-CC systems have been widely developed, research suggests that human factors underlying effective collaboration with creative AI remain under explored compared to system development itself \parencite{lin_beyond_2023}.

Beyond creative domains, HAC is also increasingly adopted in practical applications such as software testing. For instance, AI-assisted approaches have been proposed to complement or replace traditional manual game testing workflows, improving efficiency and coverage \parencite{zhang_human-ai_2025}.

Furthermore, HAC has been investigated in safety-critical domains such as autonomous driving, where human-AI collaboration is used to support decision-making and enhance system robustness. These studies highlight the potential for synergistic interaction between human operators and AI agents across diverse application areas \parencite{gao2025humancenteredhumanaicollaborationhchac}.

In the context of this study, an AI agent designed for drone piloting can provide reflective feedback to the learner. Such feedback supports cognitive reflection and facilitates the formation of abstract conceptualization, which corresponds to the second stage of Kolb's experiential learning cycle \parencite{kolb1984}.
